Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-09-28 paper/sections/proof-reconstruction.tex
[ paper ] cosmetics for theorems.
[ paper ] normalization, first part, added.

\begin{align}
\label{eq:unshunt-structured}
\begin{split}
&\unshunt_{1}(φ, \zero) = φ\\
&\unshunt_{1}(φ, \suc(n)) =\\
&\hspace{3mm}\begin{cases}
\unshunt_{1}((φ₁ ∧ φ₂) ⇒ φ₃, n),
  &\text{if } φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
\unshunt_{1}(φ₁ ⇒ φ₂, n) ∧\ \unshunt_{1}(φ₁ ⇒ φ₃, n),
   &\text{if } φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃).
\end{cases}
\end{split}
\end{align}

@@

\subsubsection{Resolve}
\label{ssub:resolve}

@@

\subsubsection{Normal Forms.}
\label{ssub:normal_forms}

@@

\begin{theorem}[thm-cnf]
\label{thm:thm-cnf}
  $Γ ⊢ φ$ then $Γ ⊢ cnf(φ)$, where,
  \begin{equation}
    cnf(φ) = (dist \circ nnf) (\varphi)
  \end{equation}
\end{theorem}

@@

\subsubsection{Clausification.}
\label{ssec:clausification}

@@

>>>>

\begin{align}
\label{eq:unshunt-structured}
\begin{split}
&\unshunt_{1}(φ, \zero)\hspace{3mm}= φ\\
&\unshunt_{1}(φ, \suc(n)) =\\
&\hspace{3mm}\begin{cases}
\unshunt_{1}((φ₁ ∧ φ₂) ⇒ φ₃, n),
  &\text{if } φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
\unshunt_{1}(φ₁ ⇒ φ₂, n) ∧\ \unshunt_{1}(φ₁ ⇒ φ₃, n),
   &\text{if } φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃).
\end{cases}
\end{split}
\end{align}

@@

\subsubsection{Resolve.}
\label{sssec:resolve}

@@

\subsubsection{Normal Forms.}
\label{sssec:normal_forms}

@@

\begin{theorem}[thm-cnf]
\label{thm:thm-cnf}
  $Γ ⊢ φ$ then $Γ ⊢ cnf(φ)$, where,
  \begin{equation}
    cnf(φ) = (dist \circ nnf) (\varphi).
  \end{equation}
\end{theorem}

@@

\subsubsection{Clausification.}
\label{sssec:clausification}

@@

% --------------------------------------------------------------------
\subsubsection{Normalization.}
\label{sssec:normalization}

In a disjunction, $φ = φ₁ ∨ φ₂ ∨ \cdots ∨ φₙ$, we say $ψ ∈_{∨} φ$,
if there is some $i = 1, \cdots, n$ such that $ψ = φᵢ$.
Then, we define the $rm_{∨}$ function to remove in a disjunction φ, those propositions ψ repeated in the formula.

\begin{equation*}
\label{eq:rm-or}
  rm_{∨}(φ) =
  \begin{cases}
    rm_{∨}(φ₂), &\text{if }φ ≡ φ₁ ∨ φ₂, φ₁ ∈_{∨} φ₂\\
    φ₁ ∨ rm_{∨}(φ₂), &\text{if }φ ≡ φ₁ ∨ φ₂\\
    φ,  &\text{otherwise.}
  \end{cases}
\end{equation*}

Since, our goal consists of normalizing prepositions in \abbre{CNF}, we also need to generalize $rm_{∨}$ to work with conjunctions. We define $rm_{∧∨}$ function for that purpose.

\begin{equation*}
\label{eq:rm-and-or}
  rm_{∧∨}(φ) =
  \begin{cases}
    rm_{∧∨}(φ₁) ∧ rm_{∧∨}(φ₂), &\text{if }φ ≡ φ₁ ∧ φ₂\\
    rm_{∨}(rconj(φ)),  &\text{otherwise.}
  \end{cases}
\end{equation*}

Now, we have removed redundancies in the disjunctions, we move forward and we remove redundancies at the level of the conjunction of the CNFs by applying the $rm_{∧}$ function, we remove conjunct repeated in the formula. We define $ψ ∈_{∧} φ$ similar as we described above for disjunction. In a conjunction, $φ = φ₁ ∧ φ₂ ∧ \cdots ∧ φₙ$, we say
$ψ ∈_{∧} φ$, if there is some $i = 1, \cdots, n$ such that $ψ = φᵢ$.

\begin{equation*}
\label{eq:rm-and}
  rm_{∧}(φ) =
  \begin{cases}
    rm_{∧}(φ₁) ∧ rm_{∧}(φ₂), &\text{if }φ ≡ φ₁ ∧ φ₂, φ₁ ∈_{∧} φ₂\\
    φ₁ ∧ rm_{∧}(φ₂), &\text{if }φ ≡ φ₁ ∧ φ₂\\
    φ,  &\text{otherwise.}
  \end{cases}
\end{equation*}

Finally, we remove redundancies in a proposition in its conjunctive normal form, by composing the functions described above in the Eq.~\ref{eq:rm-cnf} for the function $cleanCNF$.

\begin{equation*}
  \label{eq:rm-cnf}
  cleanCNF = rm_{∧} ∘ rm_{∧∨} ∘ rconj ∘ cnf.
\end{equation*}

% subsection normalization (end)
% --------------------------------------------------------------------
